Predicting Diamond Pricing: A Generalized Linear Model Analysis

### 2024-12-04 paper/paper.qmd
update data measurement

---
title: "my title"
subtitle: "subtitle"
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: "4 sentence"
format: pdf
number-sections: true
bibliography: 
  - references .bib
toc: true
---

@@

@@

@@

ggplot(data = test_data, aes(x = 1:nrow(test_data))) +
  geom_line(aes(y = predicted_price), color = "lightblue", size = 1, linetype = "solid") + 
  geom_point(aes(y = price), color = "palevioletred", size = 2) + 
  labs(
    x = "Index",
    y = "log(scale(Price)"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

>>>>

---
title: "Predicting Diamond Pricing: A Generalized Linear Model Analysis"
subtitle: "Carat Weight Dominates While Cut Plays a Smaller Role in Determining Price"
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: "This paper investigates how the Four Cs—carat weight, color, clarity, and cut—affect diamond pricing and develops a predictive model using a Generalized Linear Model (GLM) with a Gamma distribution. The analysis shows that carat weight has the strongest positive influence on price, followed by clarity and color, while cut has a relatively smaller impact. The model demonstrates robust performance, providing a reliable framework for forecasting diamond prices and understanding market patterns. These findings enhance pricing transparency, help the diamond industry adapt to shifting consumer preferences, and offer valuable insights into the economic and cultural factors shaping diamond valuation."
format: pdf
number-sections: true
bibliography: 
  - references .bib
toc: true
---

@@

The reason that I chose DASL is its directness and openness of data. The data set focuses on the diamond market, contains detailed 4C attributes and prices, directly supports the research objectives, and is completely open, ensuring the repeatability and transparency of the analysis. Additionally, there does not exist other data set about diamond price in the data set licensed in @tellingstories. However, we can find data about diamond prices from diamond retailers (such as Blue Nile or James Allen). However, these data sets usually come from commercial use, so they may have deviations from the inventory or pricing strategies of specific retailers. This deviation will limit the universality of the research results in a wider market. In addition, there may be some access restrictions to obtain the complete version of these data.

@@

Furthermore, @diamonds_data comes from the data crawled by Lou Valente of JMP from the Internet, and is arranged into a form suitable for educational and research purposes. This data collection method shows that the data may be collected from publicly available diamond market information or industry-related websites (such as retailer data or industry reports), and then cleaned and structured to ensure that it is suitable for statistical analysis and modeling tasks.

@@

ggplot(data = test_data, aes(x = 1:nrow(test_data))) +
  geom_line(aes(y = predicted_price), color = "lightblue", size = 1, linetype = "solid") + 
  geom_point(aes(y = price), color = "palevioletred", size = 2) + 
  labs(
    x = "Index",
    y = "Price"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_y_continuous(breaks = NULL)
